RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2014-08-07 manuscripts/manuscript.tex
fix figure caption
suggest phylobase (for citation at least), fix install.packages line

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{install.packages}\NormalTok{(}\StringTok{"RNeXML"}\NormalTok{, }\DataTypeTok{dependencies=}\KeywordTok{c}\NormalTok{(}\StringTok{"DEPENDS"}\NormalTok{, }\StringTok{"IMPORTS"}\NormalTok{, }\StringTok{"SUGGESTS"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-unnamed-chunk-31.pdf}
\caption{plot of chunk unnamed-chunk-31}
\end{figure}

@@

The \texttt{RNeXML} package is available through the CRAN repository
under a CC0 license. At the time of writing, the current version is
1.1.1. The current development branch can be found on Github at
{[}\url{https://github.com/ropensci/RNeXML}{]}. See the NEWS file for
changes in recent versions. Users are encouraged to submit bug reports
or feature requests in the issues log. Contact
\texttt{ropensci-discuss@googlegroups.com} or the package maintainer for
help, or email the phylogenetics R users group list at
\texttt{r-sig-phylo@r-project.org}.

>>>>

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{install.packages}\NormalTok{(}\StringTok{"RNeXML"}\NormalTok{, }\DataTypeTok{dependencies=}\OtherTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-Figure1.pdf}
\caption{Stochastic character mapping on a phylogeny, as generated by
the phytools package after parsing the simmap-extended NeXML.}
\end{figure}

@@

The \texttt{RNeXML} package is available through the CRAN repository
under a CC0 license. At the time of writing, the current version is
1.1.3. The current development branch can be found on Github at
{[}\url{https://github.com/ropensci/RNeXML}{]}. See the NEWS file for
changes in recent versions. Users are encouraged to submit bug reports
or feature requests in the issues log. Contact
\texttt{ropensci-discuss@googlegroups.com} or the package maintainer for
help, or email the phylogenetics R users group list at
\texttt{r-sig-phylo@r-project.org}.
